\mytitle

### 2012-02-22 papers/SAS2012/implicitization.tex
Fusion des deux tableaux benchmarks

\begin{table}[!h]
	\centering
\begin{tabular}{|l|r|r|} \hline
	\multicolumn{1}{|c|}{Name} &
        \multicolumn{1}{c|}{kLOC} &
        \multicolumn{1}{c|}{$|P_R|$} \\ \hline
	a2ps & 55 & 2012\\
	gawk & 59 & 902\\ 
	gnuchess & 38 & 1222\\ 
	gnugo & 83 & 2801\\
	grep & 35 & 820\\
	gzip & 27 & 494\\
	lapack/blas & 954 & 16422\\
	make & 34 & 993\\ 
	sed & 23 & 292\\
	tar & 73 & 1712\\
	\hline
\end{tabular}
\caption{List of analyzed open-source projects, with their respective number of
lines of code, and their number of control points in $P_R$}
\label{fig:projects}
\end{table}

@@

The analysis using disjunctive invariants greatly improves the
precision of the analysis (for $12.06\%$ of the control points in $P_R$), at an
acceptable time cost (see Table \ref{tab:time}).

@@

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} are sometimes faster than the classical
algorithm.
This seems due to the fact that these algorithms start on a small subset
of the graph, and then may need fewer iterations on the complete graph.
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.

\begin{table}[!h]
	\centering
\begin{tabular}{|l|r|r|r|r|r|} \hline
	\multicolumn{1}{|c|}{Benchmark} &
        \multicolumn{1}{c|}{\textbf{S}} &
        \multicolumn{1}{c|}{\textbf{G}} &
        \multicolumn{1}{c|}{\textbf{PF}} &
        \multicolumn{1}{c|}{\textbf{G+PF}} &
	\multicolumn{1}{c|}{\textbf{DIS}} \\ \hline
	\input{table_time.tex} \hline
\end{tabular}
\caption{Execution time for each technique, expressed in seconds}
\label{tab:time}
\end{table}

>>>>

\begin{table}[!h]
      \centering
      \begin{tabular}{|l|r|r|r|r|r|r|r|} \hline
        \multicolumn{1}{|c|}{} &
        \multicolumn{2}{c|}{Size} &
        \multicolumn{5}{c|}{Execution time (seconds)} \\ \hline
        \multicolumn{1}{|c|}{Name} & 
        \multicolumn{1}{c|}{kLOC}  & 
        \multicolumn{1}{c|}{$|P_R|$}  &
        \multicolumn{1}{c|}{\textbf{S}} &
        \multicolumn{1}{c|}{\textbf{G}} &
        \multicolumn{1}{c|}{\textbf{PF}} &
        \multicolumn{1}{c|}{\textbf{G+PF}} &
	\multicolumn{1}{c|}{\textbf{DIS}} \\ 
        \hline
        % M-x align RET powers ;-).
a2ps-4.14      & 55  & 2012  & 64  & 17  & 66   & 175  & 512   \\
gawk-4.0.0     & 59  & 902   & 59  & 8   & 18   & 43   & 129   \\
gnuchess-6.0.0 & 38  & 1222  & 112 & 21  & 122  & 374  & 866   \\
gnugo-3.8      & 83  & 2801  & 155 & 31  & 128  & 382  & 1403  \\
grep-2.9       & 35  & 820   & 50  & 12  & 21   & 58   & 307   \\
gzip-1.4       & 27  & 494   & 63  & 12  & 36   & 97   & 617   \\
lapack-3.3.1   & 954 & 16422 & 721 & 246 & 2690 & 6052 & 22222 \\
make-3.82      & 34  & 993   & 22  & 7   & 32   & 83   & 255   \\
sed-4.2        & 23  & 292   & 35  & 7   & 23   & 69   & 521   \\
tar-1.26       & 73  & 1712  & 270 & 39  & 110  & 304  & 1164  \\
% TODO: mettre à jour les chiffres ?
	\hline
\end{tabular}
\caption{List of analyzed open-source projects, with their respective number of
lines of code, and their number of control points in $P_R$}
\label{fig:projects}
\end{table}

@@

The analysis using disjunctive invariants greatly improves the
precision of the analysis (for $12.06\%$ of the control points in $P_R$), at an
acceptable time cost (see Table \ref{tab:time}). \MM{TODO}

@@

Table \ref{tab:time} \MM{TODO} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} are sometimes faster than the classical
algorithm.
This seems due to the fact that these algorithms start on a small subset
of the graph, and then may need fewer iterations on the complete graph.
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.
